Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-11-03 bbbq_article.tex
Added stubs of new figures

%
% Figure 2
%
\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/results.png}
  \caption{
    \textbf{
      Robust prediction that TMH epitopes are presented \emph{in vivo}.
    }
    Bars show the percentage of naturally ocurring peptides
    that are derived from a TMH. These percentages are shown for
    both MHC-I and -II (the columns), two sources of data (the
    rows) and two TMH prediction tools (the two bars). 
    IEDB = the Immune Epitope Database, non-IEDB = 
    \cite{schellens2015comprehensive} for MHC-I and
    \cite{bergseng2015different} for MHC-II.
  }
  \label{fig:elution}
\end{figure}

@@

See supplementary Table \ref{tab:elution} 
for the percentages of epitopes derived from a TMH 
found in the two elution studies, 
for the two different kind of topology prediction tools.

@@

>>>>

%
% Figure 2
%
\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/figure_2a.png}
  \caption{
    \textbf{
      Robust prediction that TMH epitopes are presented \emph{in vivo}.
    }
    The percentage of epitopes for MHC-I and -II alleles 
    that overlap with TMHs for the proteomes of human
    that is predicted 
    (outer bars, same as figure 1A for human only) 
    and is observed to occur naturally (inner bars/lines)
    (from elution studies)
    per MHC allele
  }
  \label{fig:elution}
\end{figure}

@@

See figure \ref{fig:elution_per_software} or
supplementary Table \ref{tab:elution} 
for the percentages of epitopes derived from a TMH 
found in the two elution studies, 
for the two different kind of topology prediction tools.

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/results.png}
  \caption{
    \textbf{
      Robust prediction that TMH epitopes are presented \emph{in vivo}.
    }
    Bars show the percentage of naturally ocurring peptides
    that are derived from a TMH. These percentages are shown for
    both MHC-I and -II (the columns), two sources of data (the
    rows) and two TMH prediction tools (the two bars). 
    IEDB = the Immune Epitope Database, non-IEDB = 
    \cite{schellens2015comprehensive} for MHC-I and
    \cite{bergseng2015different} for MHC-II.
  }
  \label{fig:elution_per_software}
\end{figure}

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/figure_2b.png}
  \caption{
    \textbf{
      Relationship between TMH epitopes that are predicted to
      be presented versus that are presented \emph{in vivo}.
    }
    \richel{Unsure if there is enough data}
  }
  \label{fig:elution_versus}
\end{figure}

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/figure_2c.png}
  \caption{
    \textbf{
      Relationship between TMH epitopes that are presented \emph{in vivo}.
    }
    \richel{TODO: MHC ligands only}
  }
  \label{fig:elution_mhc_ligands}
\end{figure}

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/figure_2d.png}
  \caption{
    \textbf{
      Relationship between TMH epitopes that are presented \emph{in vivo}
      in T cells.
    }
    \richel{Must mere T cell data to get more data}
  }
  \label{fig:elution_versus}
\end{figure}
